archivo de trabajo

### 2021-04-27 final/script.Rmd
Update script.Rmd

@@

JUSTIFICACIÓN CYNTHIA:

En suma, la Refoma, al mejorar las condiciones de competencia, permitió a México, ampliar el proceso de universalización de Internet, y escalar en el índice de accesibilidad a Internet: según el índice de accesibilidad de la OECD, en 2012, el 26% de los hogares mexicanos tenían acceso a internet y en 2019, 56.4%, es decir, un aumento mayor al doble.

@@

Furthermore, the specific conditions affecting the Mexican telecommunications sector over the past years
have represented an additional barrier to these households gaining Internet access (Cave & Mariscal, 2020; Ayala, Chapa, García, &
Hibert, 2018).1 Until 2013, Mexico’s telecommunications sector was concentrated in a single dominant firm (Ovando & Olivera,
2018). This market concentration, in conjunction with high connectivity costs and weak regulating agencies, explain why in 2017
Mexico’s Internet penetration rate was only 63.9% (ITU, 2017). Approximately 50% of households lack access to an Internet service at
home, yet the rural sector shows a clear disadvantage in terms of Internet access; the rate of Internet adoption in Mexico’s rural sector
was 39%, while for the urban sector this percentage increased to 71.2%

Although in recent years the greatest penetration of ICT in Mexico has been through mobile telephones,3 most of the effects on the
dimensions of poverty, such as educational backwardness, access to medical services, and access to basic housing services, may be
linked in their majority to the increased investments in infrastructure to improve Internet access beyond the individual level, as in the
case of mobile telephones.

the impact of Internet access on poverty reduction, as determined by our study, reinforces the idea that universalizing access to this service contributes to improving the welfare of a nation’s inhabitants. The results of Internet access in the Mexican population show, with high statistical reliability, that this service is a tool which can help decrease the number of poor people and could therefore become a mechanism to improve the poverty indicators recorded in medium- and low-income countries around the world

>>>>

En suma, la Refoma, al mejorar las condiciones de competencia, permitió a México, ampliar el proceso de universalización de Internet, y escalar en el índice de accesibilidad a Internet: según el índice de accesibilidad de la OECD, en 2012, el 26% de los hogares mexicanos tenían acceso a internet y en 2019, 56.4%, es decir, un aumento mayor al doble. Sin embargo, el entorno rural se encuentra en particular desventaja: su adopción es de 39%, mientras que en el entorno urbano es de 71.2%.

@@

@@
